A Hedonic Price Analysis of Traffic Noise in the Twin Cities Housing Market

### 2013-06-26 reports/Draft.Rnw
updated the draft in preparation for meeting with Tsegaye

\documentclass{article}
\usepackage[round]{natbib}
\usepackage{amsmath, graphicx}

\title{A Hedonic Price Analysis of Traffic Noise in the Twin Cities Housing Market}
\date{}
\begin{document}
\maketitle

\section{Introduction}

\begin{itemize}
\item Introduction to environmental amenities of a property
\item Outline how the impact of environmental quality on the value of a property is specific depending on locational factors.
\item Intro to traffic noise as an environmental good.
\item Brief description regarding the negative impacts of traffic noise (brief summaries of past studies on the topic)
\item Outline how traffic noise is measured – decibel levels on a logarithmic scale
\item Description of the housing market crash in the fall of 2008
\item How the crash effected Twin Cities metro real estate market
\item Research question: Does traffic noise have a significant impact on properties within the Twin Cities’ metro real-estate market and if so, does this effect vary across space while accounting for time?
\end{itemize}

\section{Past Research}\label{sec:lit}
The value of noise pollution is typically estimated through simulated or related markets because no explicit private market for noise abatement exists. \citet{Nelson1982} is perhaps the best known earliest review of 14 studies of the economic impact of traffic noise on property values in Canada and the United States. More recently, a number of reviews have been produced for European government agencies. \citet{Bateman2001} reviewed the literature for the Scottish Government while \citet{Navrud2002} provided a ``state of the art'' review for the European Commission Environment Directorate General.

The Hedonic Price Method is commonly used to value noise by examining real estate price fluctuations as a function of noise levels. Based on the canonical work by \citet{Rosen1974}, researchers commonly estimate a hedonic price function specifying the logged sale price of a property as a linear function of the traffic noise exhibited at the house. Such a specification leads to reporting the impact of traffic noise as a percentage decrease in house price per one decibal (dB) increase in traffic noise. According to \citet{Batemen2001}, the negative effect of traffic noise has ranged from 0.08\% to 2.22\% per dB with a mean around 0.55 percent per dB. \citet{Navrud2002} found an average decrease of 0.64\% per dB in a review of 65 noise evaluation studies.

\citet{Nelson2008} produced an updated review of the traffic noise literature for the edited volume \underline{Hedonic Methods in Housing Markets Economics}. Nelson describes several areas of continued interest in the empirical literature, most notably: spatial modeling of the hedonic price function, long-run vs. short-run housing dynamics, and the appropriate measure of traffic noise. We now explain each of these areas in turn and our work's contribution to the field.

@@

One common reason for significant spatially autocorrelated error terms is hedonic function misspecification. First, a portion of the hedonic regression errors may be explained by omitted spatial variables. Thus, nearby houses will tend to have similar spatial variable values and then similar error terms. Second, model misspecification can occur due to spatial non-stationarity of the hedonic function. That is, housing submarkets exist and the impact of changing housing characteristics will vary across submarkets. Failing to properly account for such heterogeneity will lead to spatially autocorrelated error estimates.

@@

\citet{Theebe2004} econometrically estimates a spatial error model

@@

\subsection{Temporal Variation}
A common strategy is to analyze cross-sectional data. However, housing transactions take place at a specific point in time and the vast majority of data sets will contain some temporal variation. Some researchers may simply assume the hedonic function is constant thoughout their timespan. Others allow the function to shift up or down through the use of temporally varying intercept terms.

Few researchers allow the hedonic function to change over time. \citet{Cho} is a recent example of work allowing the hedonic regression coefficients to change over time, thereby estimating the changes in the implicit prices of hedonic characteristics over time.

\citet{Wilhelmsson2000} split his 290 Swedish house sales into two separate time periods: 1986-89 and 1990-95. A Chow test revealed that the impact of traffic noise was different in the earlier vs. later time period, with noise being considered more of a nuisance in the 1990s in the suburb of Stockholm.

We estimate regression coefficients using only sales within the past 12 months over the years 2005 - 2010. Such an analysis allows us to see if and when the implicit price of traffic noises changes within our study area.

\citet{HughsSirmans} use traffic volume.

Spatial resolution

\section{Data}
The 2010 US Census lists the population of the Minneapolis and St. Paul Metropolitan area in Minnesota as almost 3 million residents spread over seven counties. This study examines single family residential home transactions in the Census-defined urban areas of the three of the seven counties – Dakota, Ramsey and Washington County (see Figure 1). We obtained data from approximately forty thousand sales transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council. In addition to the geographic location and date of the house sale, we collected structural and locational variables commonly used in the hedonic literature. See Table 1 for a complete list of the explanatory variables and their descriptive statistics.

@@

\subsection{Noise Data}
Insert noise data description and methodology here.

@@

\subsection{Time}
Given that we have data from before and after the recession of 2008-09, we subset the data in Table 2 by year of sale to look for differences. In addition to the noticeable decline in nominal sales values, there is also a drop in the number of sales across years. For example, in 2010 there were only 4,206 property sales within the dataset, a more than 50\% reduction from 2005. While the mean sale price declined from roughly \$280,000 pre-crash to \$230,000 post-crash, most of the structural and neighborhood variables are relatively consistent across years. However, traffic noise displays a noticeable difference in the pre- and post-crash market transactions (the mean drops from 58 dB to 52 dB).

\section{Basic Econometric Model}\label{basicModel}
Consistent with past research, this study implements a semi-logarithmic hedonic pricing model. Our aim is to estimate the marginal willingness to pay for different attributes, in particular changes in the traffic noise associated with the house. Equation~\eqref{eq:model} expresses the basic hedonic model.
\begin{equation}\label{eq:model}	
ln \textrm{ Sale Price}_i = \beta _0 + \beta _1 \textrm{Noise}_i+ \beta _2 S_i+ \beta _3 N_i + \beta _4 T_i + \textrm{error}_i
\end{equation}
Where Noise$_i$ is the noise level for house $i$, $S_i$ is a vector of the house's structural attributes, $N_i$ is a vector of the neighborhood attributes, and $T_i$ is a vector of year fixed effects. We can interpret the regression model coefficients as the price semi-elasticities of the underlying attributes. For instance, we can interpret the coefficient on noise as the percentage increase in price for a one decibal increase in the traffic noise associated with the transaction in our dataset.

Standard urban economic theory\footnote{Cite Muth, Mills, etc. here.} predicts that the price of land will vary over space within our dataset to account for locational ameinities. As such, we add interaction terms between lot size and distance to the nearest central business district to account for spatial variation in the price of land. The first column in Table XXX shows the results of this regression. The negative coefficient of -0.0027 on the noise variable (a one dB increase in noise decreases house price by 0.27 percent) is in line with the estimates described earlier in the literature. The significant coefficients on the lot size interaction terms suggest that the value of land varies over space. The significant coefficients on the non-linear interaction terms suggests that the nature of the spatial variation in the value of land may be complex.

Table XXX also attempts to begin to understand how the economic recession may have influenced the hedonic function in our study area. The other columns in the table show the regression output from separating the data into sales before and after September of 2008 (the month that the US Federal government took over Fannie Mae and Freddi Mac, Lehman Brothers filed for bankruptcy, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government). The coefficients for some of the hedonic variables of interest (noise, schools, land, for instance) appear different across the two time periods.

Taken in aggregate, the results in Table XXX suggest that the hedonic price function may vary over space and time. While methods exist for parameterizing this variation (such as spatial expansion as suggested by \citet{Casetti1974}), we have no a priori knowledge of how to parameterize the variation over space and time. As such, we turn to a semi-parametric form of hedonic regression, a flexible modeling approach which lets the data reveal how relationships vary, rather than specifying them beforehand.

\section{Locally Weighted Regression Model}
Locally Weighted Regression (LWR) techniques (also known as Geographically Weighted Regression) are described in detail by \citet{Brunsdon1998b}. It is a weighted least squares methodology in which regression coefficients are estimated over space as a function of the local data as described in Equation~\eqref{eq:LWRbeta},
\begin{equation}\label{eq:LWRbeta}
\hat{\beta}_i = (X'W_iX)^{-1}X'W_iY,
\end{equation}
where X is a $n \times m$ matrix of independent variables, $W_i$ is the $n \times n$ weights matrix, and Y is the $n \times 1$ vector of dependent variable values. The weights matrix, $W_i$ is a diagonal matrix where element $w_{jj}$ denotes the weight that the $j^{th}$ data point will receive in the regression coefficients estimated at location $i$ in the dataset. We employ a bi-square weights function and a k-nearest neighbor bandwidth approach as described in equation~\eqref{eq:weights}, 
\begin{equation}\label{eq:weights}
w_{jj}=\left[1-\left(\frac{d_{ij}}{d_{k}}\right)^2 \right]^2 \textrm{ if  }d_{ij}<d_{ik}\textrm{, otherwise = 0},
\end{equation}
where $d_{ij}$ denotes the distance between observations $i$ and $j$, and $d_{ik}$ is the distance from observation $i$ to the $k^{th}$ nearest observation. This function assigns weights close to 1 for data points near observation $i$, weights positive but closer to zero for observations farther away, and zero for all $n-k$ observations farther away than the $k^{th}$ nearest observation. 
We estimate LWR coefficients using bandwidths ranging from as small as 50 observations and as large as 10,000 observations. We choose the LWR bandwidth my minimizing the Generalized Cross Validation score as detailed in equation~\eqref{eq:GCV},
\begin{equation}\label{eq:GCV}
n*\sum_{i=1}^{n}\frac{(y_i-\hat{y}_i)^2}{(n-v_1)^2}, 
\end{equation} 
where $y_i$ is the dependent variable value, $\hat{y}_i$ is the predicted dependent variable value for observation $i$, and $v_1$ is the ``effective number of model parameters.''
$v_1=$tr(\textbf{S}), where the matrix \textbf{S} is the ``hat matrix'' which maps $y$ onto $\hat{y}$,
                   \begin{equation*}
                   \hat{y}=\textbf{S}y,
                   \end{equation*}
                   and each row of \textbf{S}, $r_i$ is given by:
                     \begin{equation*}
                   r_i=X_i(X'W_iX)^{-1}X'W_i.
                   \end{equation*}                
\section{Results}
Similar to the basic econometric model described in Section \ref{basicModel}, the LWR model estimates the logged sales price of a house as a function of structural, locational and temporal variables. In order to account for changing market conditions over time in our data, when estimating LWR coefficients we use only houses sold within the past 12 months. Thus, the coefficient estimates at a particular house are estimated using data from other sales nearby in both time and geography. We also estimated the models using sales within the past 6 and 24 months.

Figure XXX shows the relationship between the number of nearest neighbors receiving positive weights in the Locally Weighted Regression and the Generalized Cross Validation score.

Regression output from the LWR model is voluminous in comparison to a standard regression model, as coefficients are estimated at each location within the dataset. We report our results in a manner similar to \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}. Table XXX displays the results of our prefered LWR model and a similar global regression model.

The first column in Table XXX displays the estimates from a standard semi-log OLS regression with traffice noise, structural characteristics, location-based amenities, and both city and year of sale dummy variables. The coefficient in the second row of the table shows the estimated impact of an additional dB of traffic noise on the natural log of the house sale price to be -.23 percent. This value is within the range of other estimates as described earlier in section \ref{sec:lit}. Coefficients for the dummy variables (on house style, city, and year of sale) are not reported for the sake of brevity, but are available upon request. The second column in the table reports the estimated coefficient standard errors. With the exception of the coefficient on the distance to the nearest park, all reported coefficients are statistically different from zero at conventional levels.

The third column displays the mean estimated coefficients from the LWR model. In this model coefficients are estimated at each observation within the dataset using the nearest 200 house sales within the past 12 months. The third column displays the standard deviation of the estimated coefficients to give a sense of how the coefficients vary when allowed to do so through the use of locally weighted regression techniques. The fourth column shows the percentage of the local regressions for which the coefficient's p-value is less than 0.1. All regressions contained statistically significant estimates of the impact of increased living space, and a majority contained significant estimates for lot size and year of construction. Roughly half of the regressions estimated an impact of traffic noise statistically different from zero, while approximately one-third of the local regressions estimated statistically significant estimates of the locational variables (school test scores, census tract median income, distance to local amenities).

@@

We believe the use of a LWR estimation procedure is appropriate after conducting two different Monte Carlo simulations with the data. In each simulation we resampled (with replacement) the location of each house in the study and then re-estimated the LWR model with the resampled data. In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales. In 100 consecutive simulations, the smallest Generalized Cross-Validation score was obtained at the largest bandwidth. In other words, the LWR model never performed better than the global model when the locations of the data were randomized. This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance.

Second, we ran a Monte Carlo simulation as described in \citet{Fotheringham2002} and performed in a similar context by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}. The simulation is as follows:
\begin{enumerate}
\item Sample with replacement the location of each data point within the study. (just as in the previous simulation)
\item Estimate a Locally Weighted Regression model on the sampled data \emph{using the optimal bandwidth calculated in original LWR model.}
\item Calculate the mean coefficient estimates as well as the standard deviation of the estimates from the sampled data LWR estimates.
\item Repeat Steps 1-3 $M$ times. (we set $M = 100$)
\item Compare the LWR coefficient means and standard deviations from the real data to the simulated values.
\end{enumerate}
Of particular interest is the standard deviation of the LWR coefficients for a variable as compared to the distribution of simulated standard deviations. If the standard deviation of the actual LWR estimates is larger than the standard deviations from the simulations, this is interpretted as evidence of spatial non-stationarity in the coefficients. The intuition is as follows. Imagine that the coefficients are constant across space. Then, running local regressions will yield different coefficient estimates across space, not because the coefficients are truly different over space, but purely due to chance and noise in the data. Resampling the location of the data and estimating LWR models repeatedly will generate a distribution of how much the coefficients will vary across space due to chance. If the standard deviation of the LWR coefficients is larger than the standard deviations seen from the resampled data, this is consistent with the hypothesis that the coefficients vary over space more than they would due to random chance and noise within the data.

>>>>

\documentclass{article}
\usepackage[round]{natbib}
\usepackage{caption, amsmath, graphicx}

\title{A Hedonic Price Analysis of Traffic Noise in the Twin Cities Housing Market}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This paper implements the hedonic price method to estimate the impact of traffic noise on properties within the St. Paul, Minnesota metropolitan real-estate market over the time period from 2005 - 2010. We use Locally Weighted Regression (LWR) estimation techniques in order to allow the hedonic function to vary over time and space. Significant evidence suggests spatial and temporal non-stationarity in the hedonic price function within our study area. In contrast to previous research, we find little evidence that the impact of traffic noise exhibits a significant non-linear relationship with the decibel level of the traffic noise, nor does the impact seem to vary over space. Our results suggest that an increase in traffic noise of one decibel decreases house prices by an average of 0.19 percent before September, 2008, and an average of 0.37 percent after September, 2008. Both of these estimates are within the range estimated by previous research on the topic in other areas.
\end{abstract}

\section{Introduction and Past Research}\label{sec:lit}
The value of noise pollution is typically estimated through simulated or related markets because no explicit private market for noise abatement exists. \citet{Nelson1982} is perhaps the best known earliest review of 14 studies of the economic impact of traffic noise on property values in Canada and the United States. More recently, a number of reviews have been produced for European government agencies. \citet{Bateman2001} reviewed the literature for the Scottish Government while \citet{Navrud2002} provided a ``state of the art'' review for the European Commission Environment Directorate General.

The Hedonic Price Method is commonly used to value noise by examining real estate price fluctuations as a function of noise levels. Based on the canonical work by \citet{Rosen1974}, researchers typically estimate a hedonic price function specifying the logged sale price of a property as a linear function of the traffic noise exhibited at the house. Such a specification leads to reporting the impact of traffic noise as a percentage decrease in house price per one decibel (dB) increase in traffic noise. According to \citet{Bateman2001}, the negative effect of traffic noise has ranged from 0.08\% to 2.22\% per dB with a mean around 0.55\% per dB. In a review of 65 noise evaluation studies \citet{Navrud2002} found an average decrease of 0.64\% per dB.

\citet{Nelson2008} produced an updated review of the traffic noise literature for the edited volume \underline{Hedonic Methods in Housing Markets Economics}. The chapter describes several areas of continued interest in the empirical literature, most notably: the appropriate measure of traffic noise, spatial modeling of the hedonic price function, and housing market dynamics. We now explain each of these areas in turn and our work's contribution to the field.

Beyond the fact that no direct natural economic markets exist in which consumers can reveal their willingness to pay to avoid traffic noise, researchers also must choose how to measure the nuisance itself. Sound levels are commonly measured in decibels (dB), but traffic noise at a house can vary significantly depending on changing traffic conditions.

Some researchers (see, for instance, \citet{HughesJr.1992}) measure the negative externality of traffic by correlating traffic volume with house prices. However, traffic may generate other externalities beyond noise (such as local air pollution and reduced safety for pedestrians and drivers). Given the interest in government policymakers in traffic noise mitigation (cite some data here), we focus on the negative externality stemming specifically from the traffic noise itself. Additionally, until 2011, the Minnesota Department of Transportation used a cost effectiveness threshold for noise mitigation of \$3,250 per dB reduced. Given that some of the benefits of noise reductions are capitalized in house prices, we are curious to see how our estimated magnitudes compare to the state cost effectiveness cutoff.

I'm going to need some help writing about noise measures. Perhaps Tsegaye can lend a hand?

\citet{Huang;Palmquist2001} collect noise data using 128 monitoring stations throughout a suburb of Seattle, WA. They use dBA $L_{10}$ as their noise measure, where $L_{10}$ denotes the value that is exceeded 10 percent of the time. They collapse the noise readings into 2.5 dBA wide bins and report noise impact estimates of roughly 1.4\% decrease in house sales price per category increase in noise (or about 0.4\% per dBA $L_{10}$).

@@

One common reason for significant spatially autocorrelated error terms is hedonic function misspecification. A portion of the hedonic regression errors may be explained by omitted spatial variables. Thus, nearby houses will tend to have similar spatial variable values and then similar error terms. Second, model misspecification can occur due to spatial non-stationarity of the hedonic function. That is, housing submarkets exist and the impact of changing housing characteristics will vary across submarkets. Failing to properly account for such heterogeneity will lead to spatially autocorrelated error estimates.

@@

\citet{Theebe2004a} econometrically estimates a spatial error model

@@

\subsection{Temporal Variation}
A common strategy is to analyze cross-sectional data. However, housing transactions take place at a specific point in time and the vast majority of data sets will contain some temporal variation in house sales. Some researchers may simply assume the hedonic function is constant thoughout their timespan. Others allow the function to shift up or down through the use of temporally varying intercept terms.

Few researchers allow the hedonic function to change over time. \citet{Cho2011b} is a recent example of work allowing the hedonic regression coefficients to change over time, thereby estimating the changes in the implicit prices of hedonic characteristics over time.

\citet{Wilhelmsson2000} split his 290 Swedish house sales into two separate time periods: 1986-89 and 1990-95. A Chow test revealed that the impact of traffic noise was different in the earlier vs. later time period, with noise being considered more of a nuisance in the suburb of Stockholm during the 1990s.

We estimate regression coefficients over time using a moving window of 12 months in the hedonic analysis over the years 2005 - 2010. Such an analysis allows us to see if and when the implicit price of traffic noises changes within our study area. Our results suggest that the percentage change in house price from an extra decibel of traffic noise actually became more negative after the Great Recession than before. These results are different from other hedonic work such as \citet{Cho2011b} who found that environmental amenities in the Nashville, TN area mattered less during the Great Recession compared to before it.

\section{Data}
The 2010 US Census lists the population of the Minneapolis and St. Paul Metropolitan area in Minnesota as almost 3 million residents spread over seven counties. This study examines single family residential home transactions in the Census-defined urban areas of three of the seven counties – Dakota, Ramsey and Washington County (see Figure 1). We obtained data from approximately forty thousand sales transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council. In addition to the geographic location and date of the house sale, we collected structural and locational variables commonly used in the hedonic literature.

\begin{figure}
\includegraphics[width = \textwidth]{../graphs/StudyArea_SaleValueDistribution}
\caption{This figure shows the spatial extent of our study area as well as the significant spatial variation in single family house sales prices.}
\end{figure}

\begin{table}
\caption{Simple Correlation Matrix of Quantitative Variables}\label{tab:cor}
\includegraphics[width = \textwidth]{../graphs/CorrelationMatrix}
\end{table}

@@

\subsection{Noise Data}
Insert noise data description and methodology here. \citet{Nega2012}

@@

\subsection{Time}
Given that we have data from before and after the recession of 2008-09, we subset the data in Table \ref{tab:SumStatsTime} by year of sale to look for differences. In addition to the noticeable decline in nominal sales values, there is also a drop in the number of sales across years. For example, in 2010 there were only 4,206 property sales within the dataset, a more than 50\% reduction from 2005. While the mean sale price declined from roughly \$280,000 pre-crash to \$230,000 post-crash, most of the structural and neighborhood variables are relatively consistent across years. However, traffic noise displays a noticeable difference in the pre- and post-crash market transactions (the mean drops from 58 dB to 52 dB).

\begin{table}
\caption{Mean Variable Values Across Time}\label{tab:SumStatsTime}
\includegraphics[width = \textwidth]{../graphs/DescriptiveStatsByYear}
\end{table}

\section{Basic Econometric Model}\label{basicModel}
Consistent with past research, this study implements a semi-logarithmic hedonic pricing model. Our aim is to estimate the marginal willingness to pay for different attributes, in particular changes in the traffic noise associated with the house. Equation~\eqref{eq:model} expresses the basic hedonic model.
\begin{equation}\label{eq:model}	
ln \textrm{ Sale Price}_i = \beta _0 + \beta _1 \textrm{Noise}_i+ \beta _2 S_i+ \beta _3 N_i + \beta _4 T_i + \textrm{error}_i
\end{equation}
Where Noise$_i$ is the noise level for house $i$, $S_i$ is a vector of the house's structural attributes, $N_i$ is a vector of the neighborhood attributes, and $T_i$ is a vector of year fixed effects. We can interpret the regression model coefficients as the price semi-elasticities of the underlying attributes. For instance, we can interpret the coefficient on noise as the percentage increase in price for a one decibel increase in the traffic noise associated with the transaction in our dataset.

\begin{table}
\caption{Basic Regression Results- Dependent Variable = $ln$ Sale Price}\label{tab:globalRegression}

\makebox[\textwidth][c]{\includegraphics[width = 1.3\textwidth]{../graphs/GlobalRegression}}
\end{table}

Standard urban economic theory\footnote{Cite Muth, Mills, etc. here.} predicts that the price of land will vary over space within our dataset to account for locational ameinities. As such, we add interaction terms between lot size and distance to the nearest central business district to account for spatial variation in the price of land. The first column in Table \ref{tab:globalRegression} shows the results of this regression. The negative coefficient of -0.0027 on the noise variable (a one dB increase in noise decreases house price by 0.27 percent) is in line with the estimates described earlier in the literature. The significant coefficients on the lot size interaction terms suggest that the value of land varies over space. The significant coefficients on the non-linear interaction terms suggests that the nature of the spatial variation in the value of land may be complex.

Table \ref{tab:globalRegression} also attempts to begin to understand how the economic recession may have influenced the hedonic function in our study area. The other columns in the table show the regression output from separating the data into sales before and after September of 2008 (the month that the US Federal government took over Fannie Mae and Freddie Mac, Lehman Brothers filed for bankruptcy, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government). The coefficients for some of the hedonic variables of interest (noise, schools, land, for instance) appear different across the two time periods.

Taken in aggregate, the results in Table \ref{tab:globalRegression} suggest that the hedonic price function may vary over space and time. While methods exist for parameterizing this variation (such as spatial expansion as suggested by \citet{Casetti1974}), we have no a priori knowledge of how to parameterize the variation over space and time. As such, we turn to a semi-parametric form of hedonic regression, a flexible modeling approach which lets the data reveal how relationships vary, rather than specifying them beforehand.

\section{Locally Weighted Regression Model}
Locally Weighted Regression (LWR) techniques (also known as Geographically Weighted Regression) are described in detail by \citet{Brunsdon1998b}. It is a weighted least squares methodology in which regression coefficients are estimated over space as a function of the local data as described in Equation~\eqref{eq:LWRbeta},
\begin{equation}\label{eq:LWRbeta}
\hat{\beta}_i = (X'W_iX)^{-1}X'W_iY,
\end{equation}
where X is a $n \times m$ matrix of independent variables, $W_i$ is the $n \times n$ weights matrix, and Y is the $n \times 1$ vector of dependent variable values. The weights matrix, $W_i$ is a diagonal matrix where element $w_{jj}$ denotes the weight that the $j^{th}$ data point will receive in the regression coefficients estimated at location $i$ in the dataset. We employ a bi-square weights function and a k-nearest neighbor bandwidth approach as described in equation~\eqref{eq:weights}, 
\begin{equation}\label{eq:weights}
w_{jj}=\left[1-\left(\frac{d_{ij}}{d_{k}}\right)^2 \right]^2 \textrm{ if  }d_{ij}<d_{ik}\textrm{, otherwise = 0},
\end{equation}
where $d_{ij}$ denotes the distance between observations $i$ and $j$, and $d_{ik}$ is the distance from observation $i$ to the $k^{th}$ nearest observation. This function assigns weights close to 1 for data points near observation $i$, weights positive but closer to zero for observations farther away, and zero for all $n-k$ observations farther away than the $k^{th}$ nearest observation. 
We estimate LWR coefficients using bandwidths ranging from as small as 50 observations and as large as 10,000 observations. We choose the LWR bandwidth my minimizing the Generalized Cross Validation score as detailed in equation~\eqref{eq:GCV},
\begin{equation}\label{eq:GCV}
n*\sum_{i=1}^{n}\frac{(y_i-\hat{y}_i)^2}{(n-v_1)^2}, 
\end{equation} 
where $y_i$ is the dependent variable value, $\hat{y}_i$ is the predicted dependent variable value for observation $i$, and $v_1$ is the ``effective number of model parameters.''
$v_1=$tr(\textbf{S}), where the matrix \textbf{S} is the ``hat matrix'' which maps $y$ onto $\hat{y}$,
                   \begin{equation*}
                   \hat{y}=\textbf{S}y,
                   \end{equation*}
                   and each row of \textbf{S}, $r_i$ is given by:
                     \begin{equation*}
                   r_i=X_i(X'W_iX)^{-1}X'W_i.
                   \end{equation*}                
\section{Results}
Similar to the basic econometric model described in Section \ref{basicModel}, the LWR model estimates the logged sales price of a house as a function of structural, locational and temporal variables. In order to account for changing market conditions over time in our data, when estimating LWR coefficients we use only houses sold within the past 12 months. Thus, the coefficient estimates at a particular house are estimated using data from other sales nearby in both time and geography.

Figure \ref{fig:GCVmodel} shows the relationship between the number of nearest houses receiving positive weights in the Locally Weighted Regression and the Generalized Cross Validation score across three different models. The first model simply uses the basic structural characteristics as the explanatory variables (size of the house in square feet, size of the lot in acres, a categorical variable denoting the architectural style of the house, and whether or not the house is owner-occupied). The second model adds locational variables to the previously described model (test scores at the local elementary school, census tract median income, and distances to the central business district, nearest park, nearest shopping center, and nearest lake). The third model adds city fixed effects. Generally speaking, the third model performs slightly better than the second model, which performs better than the first model. The minimum GCV score is obtained using a bandwidth of 200 nearest houses and Model (3).
\begin{figure}
  \makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/GCVbyModel}}
\caption{This figure shows the relationship between bandwidth size and the GCV score for three different Locally Weighted Regression (LWR) models. For comparison, the GCV scores for each model when estimated at a global scale are also shown. Note that the LWR models all have significantly smaller GCV scores than the global models. The minimum GCV score is obtained by LWR Model (3) at a bandwidth of 200 nearest houses.}\label{fig:GCVmodel}
\end{figure}

Figure \ref{fig:GCVmodel} also displays the GCV scores for the three models estimated at the global scale. The GCV scores for the global models follow a similar patter as the LWR models, with Model (3) performing better than Model (2) and Model (1) having the highest GCV score. It is also worth noting that the LWR models have significantly lower GCV scores for a range of bandwidths when compared to the global models. These results suggest that it is important to model our data in a spatially explicit manner.

Regression output from a LWR model is voluminous in comparison to a standard regression model, as coefficients are estimated at each location within the dataset. We report our results in a manner similar to \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}. Table \ref{tab:mainresults} displays the results of LWR Model 3 and the similar global regression model. Again, note that the LWR model yields a substantially smaller GCV score (0.027 vs. 0.041).

% latex table generated in R 2.15.2 by xtable 1.7-0 package
% Mon Jun 24 16:36:58 2013

\begin{table}[ht]
\caption{Hedonic Regression Results (dependent variable = $ln(\textrm{Sale Price})$)} \label{tab:mainresults} 
\makebox[\linewidth]{
\small
\begin{tabular}{lrrrrrr} \\
 & \multicolumn{2}{c}{Global Model} & \multicolumn{4}{c}{Locally Weighted Regression Model} \\
 & \multicolumn{1}{c}{$\hat{\beta}$} & \multicolumn{1}{c}{$\hat{\sigma}_{\hat{\beta}}$} & mean $\hat{\beta}$ & \multicolumn{1}{c}{$\sigma_{\hat{\beta}}$} & (5) & (6) \\ 
  \hline
(Intercept) & 8.4E+00 & 1.3E-01 & 2.9E+00 & 1.5E+01 & 0.64 & 0.00 \\ 
  Traffic Noise & -2.6E-03 & 1.6E-04 & -2.5E-03 & 3.0E-03 & 0.47 & 0.67 \\ 
  House Size & 3.0E-04 & 2.7E-06 & 2.6E-04 & 9.1E-05 & 1.00 & 0.00 \\ 
  Lot Size & 2.6E-01 & 1.5E-02 & 4.0E-01 & 3.7E-01 & 0.67 & 0.00 \\ 
  Year of Construction & 1.2E-03 & 6.5E-05 & 4.5E-03 & 5.4E-03 & 0.79 & 0.00 \\ 
  Owner Occupancy & 2.7E-02 & 3.2E-03 & 2.3E-02 & 6.4E-02 & 0.37 & 1.00 \\ 
  Elementary Test Scores & 1.5E-03 & 1.2E-04 & 2.4E-04 & 3.1E-02 & 0.30 & 0.00 \\ 
  Median Income & 3.3E-06 & 7.7E-08 & 9.6E-07 & 8.1E-06 & 0.35 & 0.00 \\ 
  distance to CBD & 1.3E-05 & 6.3E-07 & 1.1E-05 & 1.0E-04 & 0.30 & 0.00 \\ 
  `` nearest Park & -3.7E-07 & 1.1E-06 & -1.6E-05 & 1.3E-04 & 0.32 & 0.00 \\ 
  `` nearest Lake & 2.5E-05 & 2.1E-06 & -2.8E-05 & 1.4E-04 & 0.35 & 0.00 \\ 
  `` nearest Shopping Center & -5.3E-06 & 1.3E-06 & 1.5E-05 & 8.8E-05 & 0.29 & 0.00 \\  
  location of sale & \multicolumn{2}{c}{city fixed effects} & \multicolumn{4}{c}{\footnotesize city fixed effects and nearest 200 sales} \\
  timing of sale & \multicolumn{2}{c}{year fixed effects} & \multicolumn{4}{c}{within last 12 months} \\
 \hline
  GCV score & \multicolumn{2}{c}{0.041} & \multicolumn{2}{c}{0.027}  &  & \\
  Moran's I statistic & \multicolumn{2}{c}{0.199} & \multicolumn{2}{c}{0.012} & & \\
\end{tabular}
}
 \caption*{\small (5) displays the proportion of $\hat{\beta}_{LWR}$ that can reject the null hypthesis of $\beta =0$.\\ (6) displays the proportion of Monte Carlo simulations with larger standard deviations of the LWR coefficients than $\sigma_{\hat{\beta}}$}
\end{table}

The first column in Table \ref{tab:mainresults} displays the estimates from a standard semi-log OLS regression with traffice noise, structural characteristics, location-based amenities, and both city and year of sale dummy variables. The coefficient in the second row of the table shows the estimated impact of an additional dB of traffic noise on the natural log of the house sale price to be -.23 percent. This value is within the range of other estimates as described earlier in section \ref{sec:lit}. Coefficients for the dummy variables (on house style, city, and year of sale) are not reported for the sake of brevity, but are available upon request. The second column in the table reports the estimated coefficient standard errors. With the exception of the coefficient on the distance to the nearest park, all reported coefficients are statistically different from zero at conventional levels.

The third column displays the mean estimated coefficients from the LWR model. In this model coefficients are estimated at each observation within the dataset using the nearest 200 house sales within the past 12 months. The fourth column displays the standard deviation of the estimated coefficients to give a sense of how the coefficients vary when allowed to do so through the use of locally weighted regression techniques.

Column (5) in Table \ref{tab:mainresults} shows the percentage of the local regressions for which the coefficient's p-value is less than 0.1. All regressions contained statistically significant estimates of the impact of increased living space, and a majority contained significant estimates for lot size and year of construction. Roughly half of the regressions estimated an impact of traffic noise statistically different from zero, while approximately one-third of the local regressions estimated statistically significant estimates of the locational variables (school test scores, census tract median income, distance to local amenities).

@@

\subsection{Does Space Matter?}
We believe the use of a LWR estimation procedure is appropriate after conducting two different Monte Carlo simulations with the data. In each simulation we resampled (without replacement) the location of each house in the study and then re-estimated the LWR model with the resampled data. In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales as before. In 100 consecutive simulations, the smallest Generalized Cross-Validation score was obtained at the largest bandwidth. The smallest of these GCV scores was 0.041, just as was the case with the global (non-LWR) model. In other words, the LWR model never performed better than the global model when the locations of the data were randomized. This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance.

Second, we ran a Monte Carlo simulation as described in \citet{Fotheringham2002} and performed in a similar context by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}. The simulation is as follows:
\begin{enumerate}
\item Sample with replacement the location of each data point within the study. (just as in the previous simulation)
\item Estimate a Locally Weighted Regression model on the sampled data \emph{using the optimal bandwidth calculated in original LWR model.}
\item Calculate the mean coefficient estimates as well as the standard deviation of the estimates from the sampled data LWR estimates.
\item Repeat Steps 1.--3. $M$ times.
\end{enumerate}
After 100 iterations of this simulation, the minimum GCV score for these resampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data. Again, this seems to suggest that our data exhibit spatial non-stationarity in the regression coefficients.

We are also interested in the standard deviation of our estimated LWR coefficients (the fourth column in Table \ref{tab:mainresults} as compared to the distribution of simulated standard deviations. If the standard deviation of the LWR estimates with the true data is larger than the standard deviations from the simulations, this is interpretted as evidence of spatial non-stationarity in the coefficients. The intuition is as follows. Imagine that the coefficients are constant across space. Then, running local regressions will yield different coefficient estimates across space, not because the coefficients are truly different over space, but purely due to chance and noise in the data. Resampling the location of the data and estimating LWR models repeatedly will generate a distribution of how much the coefficients will vary across space due to chance. However, if the standard deviation of the LWR coefficients is larger than the standard deviations seen from the resampled data, this is consistent with the hypothesis that the coefficients vary over space more than they would due to random chance and noise within the data.
